---
title: "Editting Presentations"
author: "PhiPrime"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## New Slide  
A new slide is denoted with a second level header, that is a new line in the `.Rmd` document starting with ##  

***
A slide without a title can be created by having a line with three asterisks, ***  

## Headings  
### A top level heading has three #s  
#### Then a subheading has four  

## Bullets  
* Bullets work just as they did in a normal R Markdown document  
  + Sub-bullets do too  
1. Ordinal lists  
3. Also work as they previously did  
2. Even correcting out of ordered listings  

## Formatting Options (1.4)  
Plain text  

*Italicized text*  

**Bold text**  

`print("Denoting code")`  

## Showing Code (1.5)  
* Just results  
```{r}
summary(mtcars$mpg)
```

* With code (`echo = TRUE`)  
```{r echo = TRUE}
summary(mtcars$mpg)
```



## Showing Code (Con't)  
* Removing comment characters (`comment = ""`)  
```{r comment = ""}
summary(mtcars$mpg)
```

* Setting `eval = FALSE` allows one to just show the code, no output  
```{r eval = FALSE, echo = TRUE}
summary(mtcars$mpg)
```

## Showing Plots  
* Show a plot with default settings  
```{r}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

## Figure Options  
* Adjust: 
  + Alignment with `fig.align`  
  + Caption with `fig.cap`  
  + Size with `fig.height` & `fig.width`  
  
```{r, fig.align = "center", fig.cap = "My Plot of Weight vs. MPG", fig.height= 3, fig.width = 3*1.618033988749}
plot(mtcars$wt, mtcars$mpg, xlab = "Weight", ylab = "MPG")
```

